%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 6CCS3PRJ Final Year Individual Project Report
% luke.day@kcl.ac.uk
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{informatics-report}
\usepackage{soul, xcolor}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{natbib} % References
\usepackage{minted} % Code listings
\usepackage[linesnumbered, ruled,noline]{algorithm2e}
\usepackage{tabularx}
\usepackage{mathtools}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\usemintedstyle{vim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Front Matter - project title, name, supervisor name and date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Code Contribution Assessment}
\author{Fahim Mohammed}
\studentID{1681338}
\supervisor{Jeroen Keppens}

\date{\today}

\abstractFile{FrontMatter/abstract.tex}
\ackFile{FrontMatter/acknowledgements.tex} %Remove line if you do not want acknowledgements

\begin{document}
\createFrontMatter
\onehalfspacing
\tableofcontents
\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Report Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can write each chapter directly here or in a separate .tex file and use the include command.

\chapter{Introduction}
The process this project sets out to analyse is known as code contributions, which help identify an author for a piece of code within a codebase and rating the individual based on the volume of said contribution in respect to the contributions of the other authors in the repository \citep{10.1007/s10664-017-9575-4}. The problem we set out to solve is relevant to student group projects where the current systems and metrics used only display a rudimentary idea of code contribution. Using this approach to code attribution can also further be applied to crowdsourced software since the public or a large community are allowed to contribute to a piece of software.

It seems that knowing what percentage of code has been generated by a particular user is a multidisciplinary interest; academic interest \citep{kilgour_gray_sallis_macdonell_2012} is obvious given the fact that most academic projects require multiple contributors. There is also a clear interest from software engineers \citep{linares-vasquez_hossen_dang_kagdi_gethers_poshyvanyk_2012} but it holds potential applications for revenue attribution to internal and open-source contributors. When it comes to student group projects, the assessor will be able attribute marks more accurately. However, the current solutions are very limited for measuring code contributions, with some approaches having limitations in accurately measuring the size of contributions \citep{git-author_2013}.

\section{Aims and Challenges}
There are numerous numbers of difficulties when measuring code contributions in a student group project when compared to a project with a single developer:
\begin{itemize}
    \item \textbf{Project Size}: Repository of code can span over multiple files and any user on the team can freely edit them. 
    \item \textbf{Code Variability}: Repository can involve a range of programming languages and different frameworks for development.
    \item \textbf{Revision Control}: Code is constantly being revised and committed by different users and the revision control software being used dictates the accuracy of the existing systems.
    \item \textbf{Ranking Metrics}: No agreed approach to metrics with existing measures not differentiating on the quality of contributions.
    \item \textbf{Perspectives}: Different individuals will have a different perspective on what is seen as an ideal ranking system.
\end{itemize}

These challenges present the problem which has yet to be applied to academic marking in group projects. This project proposes a ranking algorithm that measures code contributions by incorporate measurements on quantity of code contributed by each user and measurements of code quality. The proposed solution from this project has the following properties:
\begin{itemize}
    \item \textbf{Language agnostic}: The algorithm can be applied to files containing any form of text from C++ code to HTML or Python. 
    \item \textbf{Independent of Size}: The size of the project does not matter whether it is over large files or over a plethora of files.
    \item \textbf{Awareness of code quality}: The algorithm quantifies the quality of contributions through the number of commits it persists through from creation.
    \item \textbf{Versatility to change}: The algorithm uses diffs like Git to track any code changes such as insertions, deletions or replacements of code. It is also able to track the movement or rearrangement of code.

\end{itemize}

\section{Report Structure}
This report will start with a short overview into the background of relevant topics, followed by a literature review of some of the relevant ranking algorithms in use for the purpose of identifying code contributions. This will be followed by the requirements set out for this project, the specification for the algorithm, and the final design of the ranking algorithm.

Then, the report will step through the process of implementation for the proposed ranking algorithm chronologically. The chapter introducing the implementation will also address any challenges encountered during development and the solutions which were created as a result. 

Following this, the report will contain a short insight into the professional concerns which could be raised when the project is applied to the student group project repositories. This will be followed by a collection of case studies that will test the algorithm on certain test cases and also multiple real student group projects of different sizes, where the results of these tests will be compared and discussed. 

Next, the outcomes of the developed software and testing will be evaluated, with the strengths and weaknesses of the whole project will be identified. Conclusively, a summary of what has been learnt throughout the project and how the project could possibly be continued in the future will be contained in the conclusion chapter.
\include{Chapters/Background}
\include{Chapters/Specifcations}
\include{Chapters/Design}
%\include{Chapters/Implementation}
%\include{Chapters/ProfessionalIssues}
%\include{Chapters/Evaluation}
%\include{Chapters/Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{agsm}
\bibliography{bibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\appendix
\include{Appendices/Appendix}
%\include{Appendices/UserGuide}
%\include{Appendices/SourceCode}
\end{document}
